\textbf{SYNOPSIS}

### 2017-05-01 conc.tex
review corrections
thesis final corrections

As future work, it would be interesting to look into the following directions:
\begin{enumerate}
\item Derive finite time bounds that show a lower Hessian estimation error for 2RDSA-IH when compared to 2RDSA and 2SPSA. 
\item Stochastic Newton methods converge faster and  are often more accurate than simple gradient search schemes. However they are computationally much costlier than first-order methods. Since first-order methods exhibit slower convergence rate and heavily depend on the step-size selection one has to resort to second-order methods for improved performance. As a future work, it would be interesting to look at  methods such as momentum descent, conjugate gradient as well as, Hessian free optimization approaches which result in faster convergence for the first-order methods and are known to be computationally cheaper than second-order methods in the deterministic optimization scenario. It would be interesting to extend those methods to the stochastic optimization setting and prove that they exhibit  faster convergence than first-order methods and result in lower computational cost. 
\item In the methods described in this thesis the perturbations used are random variables. In \cite{bhatnagar2003two}, for the first-order SPSA method,  construction of two different deterministic  perturbation schemes was proposed and  under certain conditions on the perturbation vectors and noise sequences, the algorithm is shown to converge. The idea behind using deterministic perturbations is to reduce the bias in the gradient estimates. It would be interesting to extend this construction to the RDSA scheme as well. And moreover this kind of construction for second-order methods is not available for both SPSA and RDSA. One can use the above ideas and show significant improvements to the existing methods.
\item From an application point of view it would be interesting to apply these methods to some interesting real world applications. It would be interesting to explore applications of  these methods  to the design of reinforcement learning algorithms.
\end{enumerate}

>>>>

As future work, it would be interesting to look into the following directions:
\begin{enumerate}
\item Derive finite time bounds that show a lower Hessian estimation error for 2RDSA-IH when compared to 2RDSA and 2SPSA. 
\item Stochastic Newton methods converge faster and  are often more accurate than simple gradient search schemes. However they are computationally much costlier than first-order methods. Since first-order methods exhibit slower convergence rate and heavily depend on the step-size selection one has to resort to second-order methods for improved performance. As a future work, it would be interesting to look at  methods such as momentum descent, conjugate gradient as well as, Hessian free optimization approaches which result in faster convergence for the first-order methods and are known to be computationally cheaper than second-order methods in the deterministic optimization scenario. It would be interesting to extend those methods to the stochastic optimization setting and prove that they exhibit  faster convergence than first-order methods and result in lower computational cost. 
\item Newton scheme is not popular due to expensive matrix inversion at each parameter update step even in deterministic scenario. Quasi-Newton schemes given by the Broyden family may be used instead. As a future work, it would be interesting to develop stochastic approximation versions of the quasi-Newton schemes.  
\item In the methods described in this thesis the perturbations used are random variables. In \cite{bhatnagar2003two}, for the first-order SPSA method,  construction of two different deterministic  perturbation schemes was proposed and  under certain conditions on the perturbation vectors and noise sequences, the algorithm is shown to converge. The idea behind using deterministic perturbations is to reduce the bias in the gradient estimates. It would be interesting to extend this construction to the RDSA scheme as well. And moreover this kind of construction for second-order methods is not available for both SPSA and RDSA. One can use the above ideas and show significant improvements to the existing methods.
\item From an application point of view it would be interesting to apply these methods to some interesting real world applications. It would be interesting to explore applications of  these methods  to the design of reinforcement learning algorithms.
\end{enumerate}

### 2017-05-01 intro.tex
thesis final corrections

where $a_n$ is the step-size that satisfies standard stochastic approximation conditions (see (A12) in Section \ref{sec:2rdsa-results}), and $\widehat\nabla f(\theta_n)$ and $\overline H_n$ are estimates of the gradient and Hessian, respectively. Thus, \eqref{eq:newton} can be considered as  the stochastic version of the well-known Newton method for optimization. Stochastic Newton methods are often more accurate than simple gradient search schemes. A key early work in stochastic Newton methods  is given in \cite{anbar1978stochastic}. A sleeker `ODE' based convergence argument might be facilitated by \cite{smale1976convergent}.

>>>>

where $a_n$ is the step-size that satisfies standard stochastic approximation conditions (see (A12) in Section \ref{sec:2rdsa-results}), and $\widehat\nabla f(\theta_n)$ and $\overline H_n$ are estimates of the gradient and Hessian, respectively. Thus, \eqref{eq:newton} can be considered as  the stochastic version of the well-known Newton method for optimization. Stochastic Newton methods are often more accurate than simple gradient search schemes. A key early work in stochastic Newton methods  is given in \cite{anbar1978stochastic} and a sleek `ODE' based convergence argument is provided in \cite{smale1976convergent}.
